Pretty darn good control: when are approximate solutions better than approximate models

### 2023-06-26 manuscript/manuscript.Rmd
erased old appendices

Policies obtained from the PPO algorithm can be ‘‘noisy’’ as their optimization algorithm is randomized (see, e.g. App. B for visualizations of the PPO policy in the ‘‘3 species, 2 fisheries, non-stationary’’ case).
We perform some interpolation using a Gaussian process regressor in order to de-noise these policies.
Specifically, we use the *GaussianProcessRegressor* object of the *sklearn* Python library with a kernel given by
\begin{align*}
  \text{RBF}(\text{length scale = 10}) + \text{WhiteNosie}(\text{noise level = 0.1}).
\end{align*}
This interpolation method is applied to scatter data of the PPO policy evaluated on 3 different grids:
One $51\times 51 \times 5$, one $51\times 5 \times 51$ and one $5\times 51 \times 51$ grid on $(X,Y,Z)$ states.\footnote{
The raw dataset is found at \textbf{TBD} in the repository with the source code and data linked above.
Scatter plots visualizing this policy are shown in App. \textbf{TBD}.
}
The length scale and noise level values of this kernel were chosen arbitrarily---no hyperparameter tuning was needed to produce satisfactory interpolation, as will be shown in the results section.

@@

## Old appendices:

## Collected time series data

In this appendix we provide a wider selection of time series taken from the same data set as Fig. \ref{fig:timeseries}.
Namely, Figs. \ref{fig:timeseries_msy}, \ref{fig:timeseries_tac} and \ref{fig:timeseries_ppo} display these time series.

## Conservative scale-downs of MSY

Here we show the performance of constant mortality policies with a fraction $\alpha$ of the MSY mortality rate (in the main text we focused on $\alpha=0.8$).
Their performance is evaluated in Fig. \ref{fig:several-tac}.
Notice the sharp transition in performance between $\alpha = 0.9$ and $0.95$.
While the behaviour of the former closely mimics, e.g., the $\alpha=0.8$ policy, the performance of the latter is essentially the same as the optimal constant mortality ($\alpha=1$, see Fig. \ref{fig:rew_len_fig}).
This points at the fact that the value of the parameter $\alpha$, although commonly chosen simply as a rule of thumb, lives on a ‘‘knife's edge,’’ small changes in this parameter may lead to drastic changes in the dynamics of the controlled system.
What is worse: the particular scale at which this transition happens is generally dependent on the system's intrinsic dynamics.
In reality, where fishery models and their respective parameters are subject to substantial uncertainty, this fact calls to question the purported additional safety obtained via these rules of thumb.

## Optimal constant escapement policy evaluation

Here we reproduce the plots from the main text for the optimal constant escapement policy to illustrate the similarity to the DRL-derived policy.

Fig. \ref{fig:esc-tuning-eval} illustrates the tuning process of finding the optimal constant escapment policy (left panel, compare Fig. \ref{fig:tuning}).
The same figure shows, in the middle panel, the reward histogram for the optimal constant escapement policy (compare Fig. \ref{fig:rew_len_fig}).
Finally, the right panel displays the same histogram for the DRL policy (reproduced from Fig. \ref{fig:rew_len_fig}).
We may see that the two policies lead to essentially the same reward distribution.

Fig. \ref{fig:timeseries_esc} displays 9 time-series for episodes controlled with the optimal constant escapement policy.
Again, this behaviour is essentially indistinguishable from the behavior of the system controlled by the DRL policy (see Fig. \ref{fig:timeseries_ppo}).

This series of figures gives evidence that, in fact, the DRL agent we have trained has obtained a policy which, effectively, acts as an optimal constant escapement policy.
Although in Fig. \ref{fig:action-X} we found some deviations from the constant escapement case (e.g. DRL was more conservative when fishing high populations), these do not seem to lead to a different dynamics.

>>>>

Policies obtained from the PPO algorithm can be ‘‘noisy’’ as their optimization algorithm is randomized (see, e.g. App. B for visualizations of the PPO policy in the ‘‘3 species, 2 fisheries, non-stationary’’ case).
We perform some interpolation using a Gaussian process regressor in order to de-noise these policies.
Specifically, we use the *GaussianProcessRegressor* object of the *sklearn* Python library with a kernel given by
\begin{align*}
  \text{RBF}(\text{length scale = 10}) + \text{WhiteNosie}(\text{noise level = 0.1}).
\end{align*}
This interpolation method is applied to scatter data of the PPO policy evaluated on 3 different grids:
One $51\times 51 \times 5$, one $51\times 5 \times 51$ and one $5\times 51 \times 51$ grid on $(X,Y,Z)$ states.\footnote{
The raw dataset is found at the data/results\_data/2FISHERY/RXDRIFT subdirectory in the repository with the source code and data linked above.
Scatter plots visualizing this policy are shown in App. B.
}
The length scale and noise level values of this kernel were chosen arbitrarily---no hyperparameter tuning was needed to produce satisfactory interpolation, as will be shown in the results section.

@@
